A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling. They found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other. \citet{Renard_1997} then recommended that it is better to select a technique which provides block permeabilities instead of one which provides uniform effective permeability.

\citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding techniques of different simulators. The paper does not describe in any detail the upscaling techniques used by the different simulators, but it provides a complete dataset for running simulations.

>>>>

\citet{Renard_1997} provided a comprehensive review of the various techniques for upscaling. They found out that the techniques classed broadly under deterministic, stochastic and heuristic complemented each other rather than antagonising each other. They also recommended to select a technique which provides block permeabilities instead of one which provides uniform effective permeability. Finally, \citet{Christie_2001SPE10Model} provided $2$ sets of problems to compare the upscaling and upgridding (\ie mesh coarsening) techniques of different simulators. The paper does not describe in any detail the upscaling techniques used by the different simulators, but it provides a complete dataset for flow simulation models' benchmarking.
